A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-08 bioc-workflow.Rmd
udpated pd section

In the code chunk below we demonstrate how to run the `phenoDisco`
function and return a novelty detection result, according to the
specified parameters. The algorithm parameters `times`, `GS` and `p`
are passed to the function, along with the `fcol` to tell the
algorithm where the input training data is contained.

@@

```{r loadPDres, include=FALSE}
load("Data/pd_runs/pd.rda")
hl <- pdRes
setStockcol(NULL)
setStockcol(paste0(getStockcol(), 70))
```

>>>>

In the code chunk below we show how to run the `phenoDisco`
function and return a novelty detection result, according to the
specified parameters. The algorithm parameters `times`, `GS` and `p`
are passed to the function, along with the `fcol` to tell the
algorithm where the input training data is contained.

@@

```{r loadPDres, echo=FALSE}
f0 <- dir(extdatadir, full.names = TRUE,
          pattern = "bpw-pdres.rds")
pdres <- readRDS(f0)
hl <- addMarkers(hl, pdres, mcol = "pd", verbose = FALSE)
setStockcol(NULL)
setStockcol(paste0(getStockcol(), 70))
```
